\documentclass[a4paper]{article}

\input{../reportPreamble}

\usepackage{caption}
\renewcommand{\thetable}{\arabic{section}.\arabic{table}}

\title{PHY 4210-01 Senior Lab \\Lab M-1: Magnetic Field Mapping}

\author{Sarah Arends \\
        Jacquelyne Miksanek \\
        Ryan Wojtyla \\ \\
        Instructor: Jerry Collins II}

\date{February 21, 2019}
\begin{document}
\maketitle

\begin{abstract}
%physics of experiment
%apparatus used
%what was measured
%Results
\qq words words words abstract
\end{abstract}

\newpage

\setcounter{tocdepth}{2}
\tableofcontents

\newpage

\section{Theory of the Experiment}
%A short presentation of the concepts and formulas related to the experiment.

\section{Hall Effect in P-Germanium}

\subsection{Task 1}

\qq The Hall voltage dependence on the current was determined while
holding the magnetic field and the temperature at a constant. Please
note that the manual called for the constant magnetic field to be held
at 250 mT, we kept our constant magnetic field at 144 mT in order to
avoid reaching the maximum amperage on the coils. The corresponding
coil current was 4 A.

\subsubsection{Data Analysis and Results}
%Graphs, figures, and tables with captions
%Results with error analysis
%Calculate discrepancies from theory
%Discuss results and uncertainties
There is a linear relationship between the Hall Voltage and the
current, which is shown by the following equation, where $\alpha$ is
the proportionality constant:
\begin{align*}
U_H = \alpha * I
\end{align*}
The obtained proportionality constant was determined to be 0.943 V/A,
and the obtained $R^2$ value was 1.
%Compare results with theory

\subsubsection{Conclusion}
%Brief summary, discussion of results and theory

\subsection{Task 2}

\qq The sample volatge as a function of the posistive magnetic field
induction was determined. The control current was held at a constant
30 mA. The change in resistance is to be compared to an increasing
field strength.

\subsubsection{Data Analysis and Results}
%Graphs, figures, and tables with captions
%Results with error analysis
%Calculate discrepancies from theory
%Discuss results and uncertainties
\qq The resultant graph shows a non-linear and quadratic change in the
resistance as a function of the increasing induced magnetic field
strength. The determined $R^2$ value was 0.969 representing a well-fit
data line.
%Compare results with theory

\subsubsection{Conclusion}
%Brief summary, discussion of results and theory

\subsection{Task 3}

\qq A constant current of 30 mA is applied and the sample voltage is
measured as a function with its temperature. The magnetic field
remains off for this task. The manuel states that the maximum
temperature to be measured is $140^o$ C. In order to not overload the
sample the maximum temperature we obtained was $110^o$ C. Note that the
maximum temperature was reached then the sample voltage was taken as
the temperature cooled.

\subsubsection{Data Analysis and Results}
%Graphs, figures, and tables with captions
%Results with error analysis
%Calculate discrepancies from theory
%Discuss results and uncertainties
\qq The reciprocal of the voltage was plotted against the reciprocal
of the temperature. The graph has a turn around point at about 3
inverse temperature where it goes from decreasing to increasing.
%Compare results with theory

\subsubsection{Conclusion}
%Brief summary, discussion of results and theory

\subsection{Task 4}

\qq The Hall voltage was measured as a function of the magnetic
induction. This time the temperature is held constant at room
temperature, and the current is held constant at 30 mA. The manuel
states that the magnetic field should start at a strength of 300 mT,
however, we started our magnetic field at 290 mT. This was done in
order to avoid overheating the coils and causing damage to the
equipment. Note that the highest current applied to the coils was 5.98
Amperes.

\subsubsection{Data Analysis and Results}
%Graphs, figures, and tables with captions
%Results with error analysis
%Calculate discrepancies from theory
%Discuss results and uncertainties
\qq The Hall voltage was plotted against the magnetic field strength
with both positive and negative polarities. The resultant graph was
linear with a $R^2$ value of 0.999 this value is representative of a
well fit data line.
%Compare results with theory

\subsubsection{Conclusion}
%Brief summary, discussion of results and theory

\subsection{Task 5}

\qq The relationship between the Hall voltage and the temperature is
determined, this time using an induced and constant magnetic
field. The manual calls for the magnetic field to be held constant at
300 mT. However, in order to avoid overheating the coils, we kept the
magnetic field constant at 145 mT. The current was kept steady at 30
mA for the entire task. The manual also states that the temperature
should reach 140^o K, however our highest temperature was 90^oK, this
was done to prevent the overheating of the sample.

\subsubsection{Data Analysis and Results}
%Graphs, figures, and tables with captions
%Results with error analysis
%Calculate discrepancies from theory
%Discuss results and uncertainties
\qq The graph demonstrates a decrease in the Hall voltage as the
temperature increases due to an increase in the number of charge
carries which causes the drift velocity of the charge to decrease.
%Compare results with theory

\subsubsection{Conclusion}
%Brief summary, discussion of results and theory

\section{Hall Effect in N-Germanium}

\subsection{Task 1}

\qq The Hall voltage dependenceon the current was determined while
holding the magnetic field and the temperature at a constant. Please
note that the manual called for the constant magnetic field to be held
at 250 mT, we kept our constant magnetic field at 144 mT in order to
avoid reaching the maximum amperage on the coils. The corresponding
coil current was 4 A.

\subsection{Task 2}

\subsubsection{Data Analysis and Results}
%Graphs, figures, and tables with captions
%Results with error analysis
%Calculate discrepancies from theory
%Discuss results and uncertainties
%Compare results with theory

\subsubsection{Conclusion}
%Brief summary, discussion of results and theory

\subsection{Task 3}

\subsubsection{Data Analysis and Results}
%Graphs, figures, and tables with captions
%Results with error analysis
%Calculate discrepancies from theory
%Discuss results and uncertainties
%Compare results with theory

\subsubsection{Conclusion}
%Brief summary, discussion of results and theory

\subsection{Task 4}

\subsubsection{Data Analysis and Results}
%Graphs, figures, and tables with captions
%Results with error analysis
%Calculate discrepancies from theory
%Discuss results and uncertainties
%Compare results with theory

\subsubsection{Conclusion}
%Brief summary, discussion of results and theory

\subsection{Task 5}

\subsubsection{Data Analysis and Results}
%Graphs, figures, and tables with captions
%Results with error analysis
%Calculate discrepancies from theory
%Discuss results and uncertainties
%Compare results with theory

\subsubsection{Conclusion}
%Brief summary, discussion of results and theory

\newpage

\section{Hall Effect in Pure Germanium}

\subsection{Determining Band Gap in Pure Ge}

\subsubsection{Data Analysis and Results}
%Graphs, figures, and tables with captions
%Results with error analysis
%Calculate discrepancies from theory
%Discuss results and uncertainties
%Compare results with theory

\subsubsection{Conclusion}
%Brief summary, discussion of results and theory

\section{Hall Effect in Pure Zinc}

\subsection{Determining Hall Constant in Pure Zn}

\subsubsection{Data Analysis and Results}
%Graphs, figures, and tables with captions
%Results with error analysis
%Calculate discrepancies from theory
%Discuss results and uncertainties
%Compare results with theory
\qq In order to determine the Hall constant $\text{R}_\text{H}$, one can
analyze the dependence of the Hall voltage on the applied field. This
was done with a constant DC current applied across the Zn sample, with
an associated random error due to the limited precision of the power
supply. The error in the slope is obtained through linear regression,
and the thickness prescribed by the sample specifications is assumed
to have no error.

\begin{center}
\begin{tabular}{|c|c|}
\hline
Slope, $b$ $\big[  \frac{\Omega \text{cm}}{\text{G}} \big] $ & $4.11 \times 10^{-13} \pm ERROR$ \topVspace \bottomVspace \\
\hline
Thickness, $d$ [m] & $2.5 \times 10^{-5} \pm 0$ \topVspace \bottomVspace \\
\hline
Sample Current, I [A] & $13.5 \pm 0.1$ \topVspace \bottomVspace \\
\hline
\end{tabular}
\label{table:zinc_RH}
\captionof{table}{Measurements and calculations used to determine the
  experimental Hall constant of pure Zinc}
\end{center}

The Hall constant of Zinc is calculated as follows.
\begin{align*}
R_H &= \big( \frac{\mu_H}{B} \big) \, \frac{d}{I} \\
    &= (b) \, \frac{d}{I} \\
    &= (4.11 \times 10^{-13}) \, \frac{2.5 \times 10^{-5}}{13.5} \\
    &= 4.11 \times 10^{-11} \; \text{Vm/TA} \\
    &\equiv 4.11 \times 10^{-13} \; \Omega \text{cm/G} \\
\end{align*}

A theoretical value for the Hall constant of Zinc, given by the third
edition of the AIP handbook, is $R_H = 3.30 \times 10^{-13} \; \Omega
\text{cm/G}$.

% Propagate error in RH experimental

% Compare theoretical and experimental


\subsubsection{Conclusion}
%Brief summary, discussion of results and theory

\section{Appendices}

\subsection{Appendix A: Data}

\subsection{Appendix B: Source Code}

\end{document}
